Outdated and License-Violating Code on Stack Overflow

### 2017-02-28 cloneoverflow-latex/cloneoverflow.tex
Fixed the number of disagreed clone candidates.

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-4}
		& & \textit{L} & \textit{S} & \\ 
		\hline 
		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & 17,801 \\
		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & 83 \\ 
		\hline
		\multicolumn{5}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$.}  \\
	\end{tabular} %
	%}
\end{table}

@@

Even choosing only the default configurations, the number of disagreed
clone pair candidates is still too large for manual inspection.
%(67,570 for $S_D$ and 632,855 pairs for $N_D$). 
We applied two filters: clone
size and similarity threshold. %, and good/ok pairs. 
For the \emph{clone size filter}, we raised the minimum clone size to 10 lines
since larger clones are more interesting, while smaller ones tend to
be false clones~\cite{Saini2016}.
% Since the 10--line threshold is already the default configuration for
% NiCad, this filter is applied to Simian only (Simian's default
% configuration has a minimum clone size of 6 lines).
The second filter, \emph{similarity threshold}, applies
only to NiCad clone pairs since Simian does not provide a similarity
configuration. 
%The last filter, \emph{good/ok pairs}, removes the clone pairs that already exist in the agreed clone sets.
%As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size and gook/ok pairs.

>>>>

\begin{table}
	\centering
	\caption{Disagreed clone pairs before and after filtering.}
	\label{tab:online_clone_pairs}
	%\small
	%	\resizebox{\columnwidth}{!}{%
	\begin{tabular}{l|r|c|c|r}
		\hline
		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-4}
		& & \textit{L} & \textit{S} & \\ 
		\hline 
		\multirow{1}{*}{$S_D$} & 55,274 & \checkmark & & 17,801 \\
		\multirow{1}{*}{$N_D$} & 620,680 & \checkmark & \checkmark & 83 \\ 
		\hline
		\multicolumn{5}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$.}  \\
	\end{tabular} %
	%}
\end{table}

@@

Even choosing only the default configurations, the number of disagreed
clone pair candidates is still too large for manual inspection
(as shown in \Cref{tab:online_clone_pairs}). 
We applied two filters: clone
size and similarity threshold. %, and good/ok pairs. 
For the \emph{clone size filter}, we raised the minimum clone size to 10 lines
since larger clones are more interesting, while smaller ones tend to
be false clones~\cite{Saini2016}.
% Since the 10--line threshold is already the default configuration for
% NiCad, this filter is applied to Simian only (Simian's default
% configuration has a minimum clone size of 6 lines).
The second filter, \emph{similarity threshold}, applies
only to NiCad clone pairs since Simian does not provide a similarity
configuration. 
%The last filter, \emph{good/ok pairs}, removes the clone pairs that already exist in the agreed clone sets.
%As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size and gook/ok pairs.
